Saint Helena Island Implementation

### 2025-05-15 Implementation doc/Draft1.Rmd
updated version

In the StrathE2E model all marine lifeforms are explicitly or implicitly accounted for, but aggregated into coarse groups or 'guilds' defined mainly by feeding characteristics and diet preferences (Figure \@ref(fig:guilds).
All state variables, except macrophytes, are expressed solely in terms of nitrogen mass.
For more information about the StrathE2E model check the [documentations](http://www.marineresourcemodelling.maths.strath.ac.uk/strathe2e/) available.

@@

Four different NEMO-ERSEM runs were used to parameterise different versions of the Saint Helena Island implementation of StrathE2E.
These four runs are a 2x2 factorial cross of two future projected scenarios (SSP1-2.6 and SSP3-7.0) with a historical hindcast from 2015, and forcing by two atmospheric CMIP6 models (CNRM-CM6-1-HR and GFDL-ESM4)
In the following sections model output was processed for a 2010-2019 baseline period, and then decadal projections from 2020-2029 until 2060-2069.

@@

The optimization process returned an overall likelihood of 0.7799 for CNRM SSP1-2.6, 0.7843 for CNRM SSP3-7.0, 0.7728 for GFDL SSP1-2.6, 0.7696 for GFDL SSP3-7.0.

@@

files <- list(
  "Files/Fitting/model_target_annualresults_plus_chi-2010-2019-CNRM-ssp126.csv",
  "Files/Fitting/model_target_annualresults_plus_chi-2010-2019-CNRM-ssp370.csv",
  "Files/Fitting/model_target_annualresults_plus_chi-2010-2019-GFDL-ssp126.csv",
  "Files/Fitting/model_target_annualresults_plus_chi-2010-2019-GFDL-ssp370.csv")

@@

```{r fitting-fig1, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit CNRM SSP1-2.6 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting/Saint_Helena_MA_MPA_2010-2019_CNRM-ssp126_compare_plot.png")
```

@@

```{r fitting-fig2, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit CNRM SSP3-7.0 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting/Saint_Helena_MA_MPA_2010-2019_CNRM-ssp370_compare_plot.png")
```

@@

```{r fitting-fig3, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit GFDL SSP1-2.6 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting/Saint_Helena_MA_MPA_2010-2019_GFDL-ssp126_compare_plot.png")
```

@@

```{r fitting-fig4, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit GFDL SSP3-7.0 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting/Saint_Helena_MA_MPA_2010-2019_GFDL-ssp370_compare_plot.png")
```

>>>>

In the StrathE2E model all marine lifeforms are explicitly or implicitly accounted for, but aggregated into coarse groups or 'guilds' defined mainly by feeding characteristics and diet preferences (Figure \@ref(fig:guilds)).
All state variables, except macrophytes, are expressed solely in terms of nitrogen mass.
For more information about the StrathE2E model check the [documentations](http://www.marineresourcemodelling.maths.strath.ac.uk/strathe2e/) available.

@@

Four different NEMO-ERSEM runs were used to parameterise different versions of the Saint Helena Island implementation of StrathE2E.
These four runs are a 2x2 factorial cross of two future projected scenarios (SSP1-2.6 and SSP3-7.0) with a historical hindcast from 2015, and forcing by two atmospheric CMIP6 models (CNRM-CM6-1-HR and GFDL-ESM4) produced by @artioli23.
In the following sections model output was processed for a 2010-2019 baseline period, and then decadal projections from 2020-2029 until 2060-2069.

@@

The optimization process returned an overall likelihood of 0.764 for CNRM SSP1-2.6, 0.767 for CNRM SSP3-7.0, 0.754 for GFDL SSP1-2.6, 0.750 for GFDL SSP3-7.0.

@@

files <- list(
  "Files/Fitting_updated/model_target_annualresults_plus_chi-2010-2019-CNRM-ssp126.csv",
  "Files/Fitting_updated/model_target_annualresults_plus_chi-2010-2019-CNRM-ssp370.csv",
  "Files/Fitting_updated/model_target_annualresults_plus_chi-2010-2019-GFDL-ssp126.csv",
  "Files/Fitting_updated/model_target_annualresults_plus_chi-2010-2019-GFDL-ssp370.csv")

@@

```{r fitting-fig1, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit CNRM SSP1-2.6 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting_updated/Saint_Helena_MA_updated_2010-2019_CNRM-ssp126_compare_plot.png")
```

@@

```{r fitting-fig2, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit CNRM SSP3-7.0 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting_updated/Saint_Helena_MA_updated_2010-2019_CNRM-ssp370_compare_plot.png")
```

@@

```{r fitting-fig3, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit GFDL SSP1-2.6 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting_updated/Saint_Helena_MA_updated_2010-2019_GFDL-ssp126_compare_plot.png")
```

@@

```{r fitting-fig4, echo=FALSE, fig.cap="Annual integrated or averaged results from the best-fit GFDL SSP3-7.0 2010-2019 stationary model variant, compared with observed data from Saint Helena MPA. Black boxes and whiskers represent the corresponding variability in measurements aggregated over the 2010–2019 period. The visualization was generated using the function e2e_compare_obs(selection='ANNUAL').", out.width = '100%'}
knitr::include_graphics("Files/Fitting_updated/Saint_Helena_MA_updated_2010-2019_GFDL-ssp370_compare_plot.png")
```
